Panel Seminars

### 2024-02-22 index.Rmd
fix index page for DNA methylation page

* [Multifactorial RNAseq analyses](DGE_comparison_v2.html)  
* Align and count RNAseq reads (coming soon!)
    * De novo, reference-based, and Tag-seq methods

>>>>

* [Multifactorial RNAseq analyses](DGE_comparison_v2.html) 
* [DNA Methylation Assessment](FUN_02_DNA_methylation.html) 
* Align and count RNAseq reads (coming soon!)
    * De novo, reference-based, and Tag-seq methods
